{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-11-18 sftrends_manu.Rnw
working on subplot map

source('R/funcs.r')
library(WRTDStidal)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(purrr)
library(tidyr)
library(Hmisc)
library(ggrepel)
@

@@

>>>>

source('R/funcs.r')
library(WRTDStidal)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(purrr)
library(tidyr)
library(Hmisc)
library(ggrepel)
library(ggtree)
@

@@

<<trndmap2, fig.height = 9, fig.width = 6, cache = T, out.width = '0.75\\textwidth', fig.cap = 'test'>>=

res = c('din', 'nh', 'no23')
mobrks <- list(c(3, 4, 5), c(6, 7, 8), c(9, 10, 11), c(12, 1, 2))
yrbrks <- c(-Inf, 1995, Inf)
molabs <- c('Spring', 'Summer', 'Fall', 'Winter')
yrlabs <- c('1976-1995', '1996-2014')
buffx = 0.00025
buffy = 0.001
cols =  c('#D53E4F', '#4DAF4A')
sz_rng = c(2, 11)
shps = c(24, 25)
ndivs = 6
strp_fl = 'lightgrey'
bar = FALSE
stat_labs = TRUE
leg = TRUE
leg_lab = 'Percent change'

# load required data
data(delt_dat)
data(delt_map)
data(mods)

# response labels 
reslabs <- list(
  shrt = c('din', 'nh', 'no23'),
  expr = c(
    'DIN', 
    expression(paste(NH [4] ^ '+')),
    expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-'))
  )
)

# make response labels
mods <- mutate(mods, reslabs = factor(resvar, levels = reslabs$shrt, labels = reslabs$expr))

##
# get a bounding box for the stations
statmeta <- select(delt_dat, Site_Code, Latitude, Longitude) %>% 
  unique

# bounding box
lims<- select(statmeta, -Site_Code) %>% 
  apply(., 2, function(x) range(x, na.rm = TRUE))
lims <- c(
  (1 + buffx) * lims[1, 2], 
  (1 - buffy) * lims[1, 1], 
  (1 - buffx) * lims[2, 2], 
  (1 + buffy) * lims[2, 1]
  )    
names(lims) <- c('left', 'bottom', 'right', 'top')

# get trends
trnds <- mutate(mods, 
  trnd = map(data, function(x){
    wrtdstrnd_sk(x, mobrks, yrbrks, molabs, yrlabs)
    })
  )

cols <- RColorBrewer::brewer.pal(11, 'RdYlGn')
pal <- colorRampPalette(rev(cols))(1000)

# convert delta map to ggplot compatible object
delt_map <- fortify(delt_map)

# base delta map
pbase <- ggplot(delt_map, aes(x = long, y = lat)) + 
  geom_polygon(aes(group = group, fill = hole), colour = "cornflowerblue") +
  theme_bw() + 
  theme(
    plot.background = element_rect(fill='transparent', 
      colour = NA),
    panel.background = element_rect(fill='transparent', 
      colour = NA),
    legend.background = element_rect(fill='transparent', 
      colour = NA),
    legend.key = element_rect(fill = 'transparent', 
      colour = NA),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    panel.grid.minor = element_blank(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank(), 
    legend.position = 'none', 
    plot.margin = grid::unit(c(3, 3, 12, 3), 'pt'), 
    axis.text.x = element_text(size = 8), 
    axis.text.y = element_text(size = 8), 
    strip.background=element_rect(fill = 'white', colour = 'white'),
    panel.border = element_rect(colour = "grey")
  ) +
  coord_fixed(ratio = 1, xlim = lims[c(1, 3)], ylim = lims[c(2, 4)]) +
  scale_fill_manual(values=c("cornflowerblue", "white"), guide="none")

yrng <- c(-5, 5)

# unnest trend summary
toplo <-select(trnds, -data) %>% 
  unnest %>% 
  select(Site_Code, resvar, reslabs, cat, ztest, perchg) %>% 
  left_join(., statmeta, by = 'Site_Code') %>% 
  data.frame %>% 
  mutate(
    rnks = scales::rescale(perchg, c(1, 1000)), 
    rnks = round(rnks), 
    cols = pal[rnks],
    ind = 1:nrow(.), 
    cattype = ifelse(cat %in% molabs, 'mo', 'yr'), 
    perchg = pmax(yrng[1], perchg),
    perchg = pmin(yrng[2], perchg)
  )

unis <- with(toplo, paste(resvar, cattype)) %>% 
  unique

sites <- unique(toplo$Site_Code)

plo_ls <- vector('list', length = length(unis))
names(plo_ls) <- unis

for(uni in unis){

  splits <- strsplit(uni, ' ')[[1]]
  resvart <- splits[1]
  cattypet <- splits[2]

  toplo_tmp <- filter(toplo, resvar %in% resvart & cattype %in% cattypet)

  bars <- setNames(lapply(sites, function(i){

    subplo <- filter(toplo_tmp, Site_Code %in% i)
    ggplot(subplo, aes(x=cat, y = perchg, fill = factor(cat))) +
      geom_bar(stat = 'identity', colour = 'black') + 
      scale_fill_manual(values = as.character(subplo$cols)) + 
      theme_tree() + 
      xlab(NULL) + 
      ylab(NULL) + 
      theme_transparent() +
      theme(plot.margin=unit(c(0,0,0,0),"mm")) + 
      scale_y_continuous(limits = yrng)

  }), sites)

  ##
  # create some plots
  pall <- pbase
  for(i in 1:length(bars)){

      nms <- names(bars)[i]
      dat <- statmeta[statmeta$Site_Code %in% nms,]
      pall <- subview(pall, bars[[i]], x = dat$Longitude, y = dat$Latitude, 0.08, 0.08)

  }

  pall <- pall + ggtitle(uni)
  plo_ls[[uni]] <- pall

}

grid.arrange(plo_ls[[1]], plo_ls[[2]], plo_ls[[3]], plo_ls[[4]], plo_ls[[5]], plo_ls[[6]], ncol = 2)
